---
title: "Alcohol vs Seat choice"
author: "Ellyn Molzer"
date: "September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference among the mean amounts of alcohol consumed per week by row.     
$H_A$: There is a difference among the mean amount of alcohol consumer per week by row.      

## Now with ggplot - first select the basic data

```{r}
```


```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is 0.000116 < 0.05 so we reject the null hypothesis 
```{r}
plot(TukeyHSD(model1))
```

## Conclusions
There is a difference between alcohol consumption and seating for front-back, there is a difference between alcohol consumption and seating for middle-back, there is no difference between alcohol consumption and seating for middle-front. 

